A formal approach but practical approach in train regulation

### 2025-06-25 paper/main.tex
Explication UntilNext

\subsection{Agents}
\paragraph{Trains.}
We now present the train model. We consider a set of $k$ trains. 
Each train is characterised by an identifier, a position, a direction, and a list of orders.
\begin{itemize}
	\item Train identifiers form a set  $\trains = \{\tid{1}, \ldots, \tid{k}\}$, each train having its own identifier.
	\item The position is the index of the block currently occupied by the train.
	\item The direction (taken from $\directions_\dirStop = \{\dirBackward, \dirForward, \dirStop\}$) indicates the direction the train is ordered to go towards, where \dirStop indicates the train has no direction order at the moment. The direction represents the current move order, but does not mean the train is actually moving: it can be blocked at a signal.
	\item Orders are a (possibly empty) sequence of orders $\su{d}{\bid{1}\dots\bid{n}}$ ($\dirFmt{d} \in \directions$, $\bid{i} \in \blocks^\star$). Such order states that the train direction is set to $\dirFmt{d}$ and that the train will use blocks $\bid{1}\dots\bid{n}$. An empty sequence is denoted $\emptyTrainProg$.
\end{itemize}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{UntilNext}] {
		\suc{\bid{id}}{d}{\switches} = \bid{id^\prime} \neq \nosuc
		\and
		\signalF{\bid{id}}{d} = \siggreen
	}{
		\redTuple{\guardT}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\trainConcat{\su{d}{[\bid{id^\prime}]}}{P}}\}}{\regulator}{\switches}{\signals}} \\
		\reduces		
		\redTuple{\guardS}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id^\prime}}{d}{P}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}
Notice that, in \ruleRef{UntilNext}, no message is added to the buffer.
\todo{@Lucas, expliquer pourquoi c'est pas nécessaire.}

>>>>

\subsection{Agents}
\paragraph{Trains.}
We now present the train model. We consider a set of $k$ trains. 
Each train is characterised by an identifier, a position, a direction, and a list of orders.
\begin{itemize}
	\item Train identifiers form a set  $\trains = \{\tid{1}, \ldots, \tid{k}\}$, each train having its own identifier.
	\item The position is the index of the block currently occupied by the train.
	\item The direction (taken from $\directions_\dirStop = \{\dirBackward, \dirForward, \dirStop\}$) indicates the direction the train is ordered to go towards, where \dirStop indicates the train has no direction order at the moment. The direction represents the current move order, but does not mean the train is actually moving: it can be blocked at a signal.
	\item Orders are a (possibly empty) sequence of orders $\su{d}{\bid{1}\dots\bid{n}}$ ($\dirFmt{d} \in \directions$, $\bid{i} \in \blocks^\star$). Such order states that the train direction is set to $\dirFmt{d}$ and that the train will use blocks $\bid{1}\dots\bid{n}$. An empty sequence is denoted $\emptyTrainProg$. We intend successive \su{d_i}{...} orders of the list to alternate directions \dirForward{} and \dirBackward{}. Two successive orders with the same direction can easily be merged into a single one.
\end{itemize}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{UntilNext}] {
		\suc{\bid{id}}{d}{\switches} = \bid{id^\prime} \neq \nosuc
		\and
		\signalF{\bid{id}}{d} = \siggreen
	}{
		\redTuple{\guardT}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\trainConcat{\su{d}{[\bid{id^\prime}]}}{P}}\}}{\regulator}{\switches}{\signals}} \\
		\reduces		
		\redTuple{\guardS}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id^\prime}}{d}{P}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}
Notice that, in \ruleRef{UntilNext}, no message is added to the buffer. since successive \su{d}{N} orders alternate directions, the next order for that train is either \ruleRef{Start} or \ruleRef{Stop}, which send the appropriate event. We prefer sending event in \ruleRef{Start} so that there is an initial event before the train initial departure.
